---
name: Robin A. Donatello
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: Dr.PH, Biostatistics
position: Associate Professor of Statistics
address: "Department of Mathematics and Statistics, \\tabularnewline California State University, Chico"
phone: 
email: rdonatello@csuchico.edu
twitter: norcalbiostat
www: norcalbiostat.com
github: norcalbiostat
linkedin: rajeffries
headcolor: 168233
output: 
  vitae::hyndman:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ dates,
    "Dr. Public Health in Biostatistics", "University of California, Los Angeles", "2007 - 2013", 
    "Masters of Science in Biostatistics", "University of California, Los Angeles",  "2005 - 2007",
    "Bachelors of Science - Statistics", "California State University, Chico",  "2001 - 2005",
    "Bachelors of Science - Biology, Minor in Chemistry", "California State University, Chico", "2001 - 2005", 
) %>% 
  detailed_entries(degree, dates, uni)
```



# Employment

```{r jobs}
tribble(
  ~ role, ~ company,  ~ dates, ~details,
  "Associate Professor", "Department of Mathematics and Statistics, California State University, Chico",  "2020 - Present", NA,
  "Assistant Professor", "Department of Mathematics and Statistics, California State University, Chico",  "2014 - 2020", NA,
  "Database Administrator", "Keeping It Real LAC" ,  "2012 - 2015", "Joint employment between the Institute for Health Promotion and Disease Prevention Research, University of Southern California and the Los Angeles County Department of Public Health, HIV and STD Program Office",
  "Data Analyst", "Project Connect, Health Research Association, University of Southern California",  "2007 - 2012",NA,
) %>% 
  detailed_entries(with  = company, 
                   what  = role, 
                   when  = dates, 
                   why   = details)
```

# Academic leadership
* **Data Science Program Coordinator** (2014-Present)
    - In collaboration with the Department of Computer Science, I developed the Undergraduate Certificate in Data Science at CSU, Chico. Program started Fall 2018
    - Currently working to expand into the Freshman/GE and Graduate space; Create a student internship program, and fee-based data-services practice. 
    - Website developer and maintainer for campus based website (https://www.csuchico.edu/datascience) and external blog based website (http://datascience.csuchico.edu)
* **DataFest Event Coordinator** (2018-Present)
  - Organize and host the annual DataFest at Chico State, a weekend long data hackathon where teams of undergraduate students tackle a suprise real world dataset and compete for fame and prizes. 
  - Website: https://chicodatafest.netlify.app/ 

# Teaching 

I teach the Intro and Applied Statistics courses for majors and non-majors, as well as an Intro and Advanced Data Science course at Chico State. Courses marked with a $^{\dagger}$ indicate that I developed and introduced that course. Most of my course materials are available on my website: www.norcalbiostat.com. 

$\vspace{1mm}$

* **Statistics** (Math 105) - General Education
* $^{\dagger}$**Introduction to R** (Math 130) - Short course
* **Applied Statistics I** (Math 315) - Non Majors, mostly Natural Sciences
* **Applied Statistics II** (Math 456) - Majors, Minors, Data Science Certificate
* $^{\dagger}$**Introduction to Data Science** (Math 385)
* $^{\dagger}$**Advanced Topics in Data Science** (Math 485)
* $^{\dagger}$**Data Science Project Capstone** (Math 490)

\newpage

## Workshops
In addition to teaching traditional courses, I occasionally teach reproducible research and data analysis skills using R at workshops.


```{r}
wk <- read.csv("workshops.csv", header=TRUE) %>% arrange(desc(when))
wk %>% 
          detailed_entries(when = when, 
                           what = title,
                           with = loc, 
                           where = org, 
                            why = details)
```

# Grants & Contracts

```{r}
gc <- read.csv("grants.csv", header=TRUE) %>% arrange(desc(dates)) %>%
       mutate(with = paste0(type, " $", amount))
gc %>% detailed_entries(when = dates, 
                        what = grant, 
                        where = title, 
                        with = with,
                        why  = details)
```

\newpage

# Consulting
I often consult with internal and external people and organizations to provide Statistical or Data Science assistance that do not directly result in a manuscript. 

```{r}
consulting <- read.csv("consulting.csv", header=TRUE) %>% arrange(desc(when))
consulting %>% detailed_entries(when = when, 
                                what = with, 
                                with = loc, 
                                why = details)
```


# Professional Society Memberships

```{r memberships}
tribble(
  ~ dates, ~ company, ~ role, ~details, 
  "2007 - Present", "American Statistical Association", 
  "Member", "Sections on Statistics and Data Science Education, 
  Statistical Programmers and Analysts, Teaching Statistics in Health Sciences",
  "2012 - 2013", "Western Users of SAS Software", 
  "Student Member", NA, 
  "2011 - 2013", "American Public Health Association", 
  "Member", "Section on Public Health Statistics"
) %>% 
  detailed_entries(what  = company, 
                   where  = details, 
                   when  = dates,
                   with = role)
```

# Professional Service

```{r}
wk <- read.csv("prof-service.csv", header=TRUE) %>% arrange(desc(dates))
wk %>% 
          detailed_entries(when = dates, 
                           what = bold, 
                          where = under, 
                            with = right)
```

\newpage

# Publications

```{r bibfiles}
pubs <- bibliography_entries("pubs.bib")
```

## Books

```{r books}
pubs %>%
  filter(bibtype == "Book") %>%
  arrange(desc(year), surnames)
```

## Peer-reviewed manuscripts

```{r papers}
pubs %>%
  filter(bibtype == "Article") %>%
  arrange(desc(year), surnames)
```

## Presentations

```{r talks}
pubs %>%
  filter(bibtype == "InProceedings") %>%
  arrange(desc(year), surnames)
```

