---
name: Robin A. Donatello
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: Dr.PH, Biostatistics
position: Associate Professor of Statistics
address: "Department of Mathematics and Statistics, \\tabularnewline California State University, Chico"
email: rdonatello@csuchico.edu
website: norcalbiostat.com
github: norcalbiostat
linkedin: rajeffries
twitter: norcalbiostat
orcid: "0000-0001-8487-5995"
headcolor: "168233"
docname: "CV_Donatello"
output: 
  vitae::hyndman:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ dates,
    "Dr. Public Health in Biostatistics", "University of California, Los Angeles", "2007 - 2013", 
    "Masters of Science in Biostatistics", "University of California, Los Angeles",  "2005 - 2007",
    "Bachelors of Science - Statistics", "California State University, Chico",  "2001 - 2005",
    "Bachelors of Science - Biology, Minor in Chemistry", "California State University, Chico", "2001 - 2005", 
) %>% 
  detailed_entries(degree, dates, uni)

tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "BCom (Hons) in Econometrics", "Monash University", "Clayton, Australia", "Mar. 2017 - Nov. 2017", 
    list("Recipient of the Econometrics Honours Memorial Scholarship, Dean's Honour, Dean's Commendation, and best in class for 5 units.",
         "Honours research project was to develop a state space model for quickly forecasting time series with multiple seasonalities.",
         "Studied units include Bayesian and frequentist econometrics, advanced statistical modelling and computational science."),
  "BCom in Econometrics, BSc in Mathematical statistics and Computational Science", "Monash University", "Clayton, Australia", "Mar. 2013 - Nov. 2016", 
    list("Recipient of the Monash Community Leaders Scholarship, International Institute of Forecasters Award, and best in class for 4 units.",
         "Mentor for the Access Monash Ambassador Program (2015 and 2016)",
         "Participant of the Vice-Chancellor's Ancora Imparo Student Leadership Program (2014)",
         "Studied a broad range of units covering many aspects of data science. The three disciplines I majored in explored different perspectives for working with data.")
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```



# Employment

```{r jobs, eval=FALSE}
tribble(
  ~ role, ~ company,  ~ dates, ~details,
  "Associate Professor", "Department of Mathematics and Statistics, California State University, Chico",  "2020 - Present", NA,
  "Assistant Professor", "Department of Mathematics and Statistics, California State University, Chico",  "2014 - 2020", NA,
  "Database Administrator", "Keeping It Real LAC" ,  "2012 - 2015", "Joint employment between the Institute for Health Promotion and Disease Prevention Research, University of Southern California and the Los Angeles County Department of Public Health, HIV and STD Program Office",
  "Data Analyst", "Project Connect, Health Research Association, University of Southern California",  "2007 - 2012",NA,
) %>% 
  detailed_entries(with  = company, 
                   what  = role, 
                   when  = dates, 
                   why   = details)


tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data scientist", "Nectric", "Melbourne, Australia", "Jan. 2019 - Present", 
    list("Data science consulting projects including spatio-temporal modelling, and large scale forecasting.",
         "Hosting workshops improving data literacy, development, analysis and modelling capabilities."
    ),
  "Research assistant", "Monash University", "Clayton, Australia", "Oct. 2015 - Present", 
    list("Involved in many internal and external data projects of varying size and complexity.", 
         "Projects typically feature large scale time series modelling or analysis, cross-sectional modelling and creating tools for improving workflows.",
         "Consulting project clients include: Huawei, Monash University, R Consortium, NSW Chief Scientist office, DiabetesLab and Tennis Australia."),
  "Teaching Associate", "Monash University", "Clayton, Australia", "Mar. 2016 - Present", "Sessional teaching of university students undertaking Bachelor's and Master's degrees. Specific classes are listed in 'Teaching experience'."
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Education

# Academic leadership
* **Data Science Program Coordinator** (2014-Present)
    - In collaboration with the Department of Computer Science, I developed the Undergraduate Certificate in Data Science at CSU, Chico. Program started Fall 2018
    - Currently working to expand into the Freshman/GE and Graduate space; Create a student internship program, and fee-based data-services practice. 
    - Website developer and maintainer for campus based website (https://www.csuchico.edu/datascience) and external blog based website (http://datascience.csuchico.edu)
* **DataFest Event Coordinator** (2018-Present)
  - Organize and host the annual DataFest at Chico State, a weekend long data hackathon where teams of undergraduate students tackle a suprise real world dataset and compete for fame and prizes. 
  - Website: https://chicodatafest.netlify.app/ 


# Teaching 

I teach the Intro and Applied Statistics courses for majors and non-majors, as well as an Intro and Advanced Data Science course at Chico State. Courses marked with a $^{\dagger}$ indicate that I developed and introduced that course. Most of my course materials are available on my website: www.norcalbiostat.com. 

$\vspace{1mm}$

* **Statistics** (Math 105) - General Education
* $^{\dagger}$**Introduction to R** (Math 130) - Short course
* **Applied Statistics I** (Math 315) - Non Majors, mostly Natural Sciences
* **Applied Statistics II** (Math 456) - Majors, Minors, Data Science Certificate
* **Probability and Statistics I** (Math 350) - Calculus based prob & stat for all math & some engineering majors.
* $^{\dagger}$**Introduction to Data Science** (Math 385)
* $^{\dagger}$**Advanced Topics in Data Science** (Math 485)
* $^{\dagger}$**Data Science Project Capstone** (Math 490)

\newpage

## Workshops
In addition to teaching traditional courses, I occasionally teach reproducible research and data analysis skills using R at workshops.


```{r}
wk <- read.csv("workshops.csv", header=TRUE) %>% arrange(desc(when))
wk %>% 
          detailed_entries(when = when, 
                           what = title,
                           with = loc, 
                           where = org, 
                            why = details)
```

# Grants & Contracts

```{r}
gc <- read.csv("grants.csv", header=TRUE) %>% arrange(desc(dates)) %>%
       mutate(with = paste0(type, " $", amount))
gc %>% detailed_entries(when = dates, 
                        what = grant, 
                        where = title, 
                        with = with,
                        why  = details)
```

\newpage

# Consulting
I often consult with internal and external people and organizations to provide Statistical or Data Science assistance that do not directly result in a manuscript. 

```{r}
consulting <- read.csv("consulting.csv", header=TRUE) %>% arrange(desc(when))
consulting %>% detailed_entries(when = when, 
                                what = with, 
                                with = loc, 
                                why = details)
```


# Professional Society Memberships
=======
## University Tutoring

<!-- My teaching quality at Monash University has been consistently recognised with positive student evaluations and individual praise from my students. I have also been awarded six congratulatory letters for outstanding student evaluations for four of my units (ETF5231, ETC3580, ETC3550, ETC5523), which indicates that student feedback for the unit is among the best in the university. -->

```{r tutoring}
tribble(
  ~ title, ~ code, ~ campus, ~ semester, ~ purple,
  "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2021 S1", NA,
  "Communicating with Data", "ETC5523", "Clayton", "2020 S2", TRUE,
  "Applied forecasting", "ETC3550/ETC5550", "Clayton", "2020 S1", TRUE,
  "Advanced statistical modelling", "ETC3580", "Clayton", "2019 S2", TRUE,
  "Data modelling and computing", "ETC1010", "Clayton", "2019 S2", FALSE,
  "Data modelling and computing", "ETC1010", "Clayton", "2019 S1", FALSE,
  "Applied forecasting for business and economics", "ETC3550/ETC5550", "Clayton", "2019 S1", TRUE,
  "Data modelling and computing", "ETC1010", "Clayton", "2018 S2", FALSE,
  "Advanced statistical modelling", "ETC3580", "Clayton", "2018 S2", TRUE,
  "Business forecasting", "ETF3231/ETF5231", "Caulfield", "2018 S1", TRUE,
  "Data modelling and computing", "ETC1010", "Clayton", "2017 S2", FALSE,
  "Business forecasting", "ETF3231/ETF5231", "Caulfield", "2017 S1", FALSE,
  "Mathematics for business", "ETF2700", "Caulfield", "2016 S2", FALSE,
  "Business forecasting", "ETF3231/ETF5231", "Caulfield", "2016 S1", FALSE
) %>% 
  brief_entries(glue::glue("\\textbf{<code>}: <title> (Monash <campus>)", .open = "<", .close = ">"), semester, .protect = FALSE)
```

\newpage

## Industry Workshops

<!-- In addition to sessional tutoring, I also teach data analysis workshops for working professionals. -->

```{r workshops}
tribble(
  ~ role, ~ course, ~ organisation, ~ country, ~ dates, ~ details,
  "Teaching assistant", "Tidy Time Series and Forecasting in R", "rstudio::conf", "USA", "Jan. 2020", "Two day workshop with Rob Hyndman on forecasting using tidyverse workflows.",
  "Instructor", "Interactive documents with Shiny", "CSIRO", "Australia", "Nov. 2019", "Two day intermediate workshop on developing of shiny applications.",
  "Instructor", "Data Wrangling", "Monash University", "Australia", "Sep. 2019", "A short workshop in the 'R Workshops for Beginners' series on using tidyr and dplyr to wrangle data.",
  "Helper", "Tidyverse developer day", "RStudio", "France", "Jul. 2019", "A one day developer day where I helped R users resolve issues on tidyverse packages.",
  "Teaching assistant", "High-dimensional time series analysis", "ISI WSC", "Malaysia", "Aug. 2019", "One day short course with Rob Hyndman for analysing and forecasting large collections of time series.",
  "Instructor", "The grammar of animation", "Monash University", "Australia", "Mar. 2019", "A short workshop for NUMBAT group on creating animated graphics in R with the gganimate package.",
  "Teaching assistant", "Master R Developer Workshop", "RStudio", "Australia", "Dec. 2016", "A two day workshop with Hadley Wicham on programming with R and developing R packages.",
) %>% 
  brief_entries(glue::glue("\\textbf{<course>}: <role> (<organisation>, <country>) \\newline <details>", .open = "<", .close = ">"), paste0(dates, "\\newline"), .protect = FALSE)
```


```{r memberships}
tribble(
  ~ dates, ~ company, ~ role, ~details, 
  "2007 - Present", "American Statistical Association", 
  "Member", "Sections on Statistics and Data Science Education, 
  Statistical Programmers and Analysts, Teaching Statistics in Health Sciences",
  "2012 - 2013", "Western Users of SAS Software", 
  "Student Member", NA, 
  "2011 - 2013", "American Public Health Association", 
  "Member", "Section on Public Health Statistics"
) %>% 
  detailed_entries(what  = company, 
                   where  = details, 
                   when  = dates,
                   with = role)
```

# Professional Service

```{r}
wk <- read.csv("prof-service.csv", header=TRUE) %>% arrange(desc(dates))
wk %>% 
          detailed_entries(when = dates, 
                           what = bold, 
                          where = under, 
                            with = right)
```

\newpage

# Publications

```{r bibfiles}
pubs <- bibliography_entries("pubs.bib")
```

## Books

```{r books}
pubs %>%
  filter(bibtype == "Book") %>%
  arrange(desc(year), surnames)
```

## Peer-reviewed manuscripts

```{r papers}
pubs %>%
  filter(bibtype == "Article") %>%
  arrange(desc(year), surnames)
```

\newpage

# Presentations

```{r talks}
pubs %>%
  filter(bibtype == "InProceedings") %>%
  arrange(desc(year), surnames)
```

<!-- # Data analysis projects -->

<!-- # Related interests -->
<!-- * Home automation -->
<!-- * Beekeeping -->
<!-- * Permaculture -->
<!-- * Electronics design -->
<!-- * Woodworking -->

<!-- # Relevant Skills -->
<!-- ```{r} -->
<!-- cvskill("Data Analysis", c("Visualisation", "Data Cleaning", "Forecasting", "Modelling", "Communication", "Inference", "Machine Learning", "Web Scraping")) -->
<!-- cvskill("Programming", c("R", "Python", "SQL", "Java", "C", "C++", "HTML/CSS", "TeX", "MATLAB")) -->
<!-- ``` -->

<!-- # Awards & Achievements -->
<!-- ## Awards -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ award, ~ from, ~ year, -->
<!--   "Commerce Dean's Honour", "Monash", "2017", -->
<!--   "Commerce Dean's Commendation", "Monash", "2016", -->
<!--   "Science Dean’s List", "Monash", "2014-2016", -->
<!--   "International Institute of Forecasters Award", "IIF", "2014", -->
<!--   "Rotary Youth Leadership Award", "Rotary", "2013" -->
<!-- ) %>% -->
<!--   brief_entries(award, year, from) -->
<!-- ``` -->



