---
name: Robin A. Donatello
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: Dr.PH, Biostatistics
position: 
address: 
phone: 
email: rdonatello@csuchico.edu
twitter: norcalbiostat
www: norcalbiostat.com
github: norcalbiostat
linkedin: rajeffries
headcolor: 1618b5
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# Education
```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~details,
    "Dr. Public Health in Biostatistics", "University of California, Los Angeles", "Los Angeles", "2007 - 2013", "Thesis: Sequential Bayesian Regression for Multiple Imputation and Conditional Editing",
    "Masters of Science in Biostatistics", "University of California, Los Angeles", "Los Angeles", "2005 - 2007",NA,
    "Bachelors of Science", "California State University, Chico", "Chico", "2001 - 2005", "Statistics", 
    "Bachelors of Science", "California State University, Chico", "Chico", "2001 - 2005", "Biology, Minor in Chemistry"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```



# Work Experience

```{r jobs}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~details,
  "Faculty in Statistics", "Department of Mathematics and Statistics, California State University, Chico", "Chico, CA", "2014 - Present", "Associate Professor (2020-Present)",
  "Faculty in Statistics", "Department of Mathematics and Statistics, California State University, Chico", "Chico, CA", "2014 - Present", "Assistant Professor (2014-2020)",
  "Faculty in Statistics", "Department of Mathematics and Statistics, California State University, Chico", "Chico, CA", "2014 - Present", "Courses Taught: Intro Statistics (GE Freshmen), Applied Statistics I (mostly non-majors), II (mostly majors), Data Science",
  "Database Administrator", "Keeping It Real LAC, Institute for Health Promotion and Disease Prevention Research, University of Southern California" , "Los Angeles, CA", "2012 - 2015", "Jointly managed by – Los Angeles County Department of Public Health, HIV and STD Program Office", 
  "Data Analyst", "Project Connect, Health Research Association, University of Southern California", "Los Angeles, CA", "2007 - 2012",NA,
) %>% 
  detailed_entries(with=company, 
                   what = role, 
                   when = dates, 
                   where = loc, 
                   why = details)
```

# Teaching 

I teach the Intro and Applied Statistics courses for majors and non-majors, as well as an Intro and Advanced Data Science course at Chico State. Most of my course materials are available on my website: www.norcalbiostat.com. 

In addition to teaching traditional courses, I occasionally teach reproducible research and data analysis skills using R at workshops.


```{r workshops}
tribble(
  ~ role, ~ course, ~ location, ~ dates, ~ details,
  "Instructor", "Promote yourself - make your own professional website without knowing HTML", "International Conference on Health Policy Statistics 2020, San Diego, California", "Jan. 2020", "https://norcalbiostat.github.io/ichps20_workshops/",
  "Instructor", "Carpentry workshop 2019", "CSU, Chico", "Nov. 2019", "Two day intermediate workshop on developing of shiny applications.",
  "Instructor", "Carpentry workshop 2018", "CSU Chico", "Sep. 2019", "A short workshop in the student ran 'R Workshops for Beginners' series on using tidyr and dplyr to wrangle data.",
  "Instructor", "That teaching thing", "CSU Chico", "Sep. 2019", "A short workshop in the student ran 'R Workshops for Beginners' series on using tidyr and dplyr to wrangle data.",
  "Helper", "Carpentry workshop 2017", "UC Davis", "Jul. 2019", "A one day developer day where I helped R users resolve issues on tidyverse packages.",
) %>% 
  detailed_entries(role, dates, course, location, details)
```

# Program Coordinator
I run the DSI. 

<!-- ## Academic research -->

```{r bibfiles}
pubs <- bibliography_entries("pubs.bib")
```

# Scholarly Works 

## Books

```{r books}
pubs %>%
  filter(bibtype == "Book") %>%
  arrange(desc(year), surnames)
```

## Peer-reviewed manuscripts

```{r papers}
pubs %>%
  filter(bibtype == "Article") %>%
  arrange(desc(year), surnames)
```

## Presentations

```{r talks}
pubs %>%
  filter(bibtype == "InProceedings") %>%
  arrange(desc(year), surnames)
```

