---
name: Robin
surname: Donatello
position: "Associate Professor of Statistics"
address: "Department of Mathematics and Statistics, California State University, Chico"
www: norcalbiostat.com
email: "rdonatello@csuchico.edu"
github: norcalbiostat
linkedin: rajeffries
twitter: norcalbiostat
orcid: "0000-0001-8487-5995"
date: "`r format(Sys.time(), '%B %Y')`"
docname: "CV_Donatello"
output: 
   vitae::moderncv:
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
library(tibble)
```

<!---
# Some stuff about me

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.
--->

# Education

```{r}
tribble(
  ~ degree, ~ uni, ~ dates,
    "Dr. Public Health in Biostatistics (DrPH)", "University of California, Los Angeles", "2007 - 2013", 
    "Masters of Science in Biostatistics", "University of California, Los Angeles",  "2005 - 2007",
    "Bachelors of Science - Statistics", "California State University, Chico",  "2001 - 2005",
    "Bachelors of Science - Biology, Minor in Chemistry", "California State University, Chico", "2001 - 2005", 
) %>% 
  brief_entries(degree, dates, uni)
```


# Employment

 
```{r jobs}
tribble(
  ~ role, ~ company,  ~ dates,
  "Associate Professor", 
    "Department of Mathematics and Statistics, California State University, Chico",  
    "2020 -", 
  "Assistant Professor", 
    "Department of Mathematics and Statistics, California State University, Chico",  
    "2014 - 20", 
  "Research Manager V", 
    "Center for Healthy Communities, Chico State Enterprises",  
    "2018 -",
  "Database Administrator", 
    "Keeping It Real LAC - Joint employment between the Institute for Health Promotion and Disease Prevention Research, University of Southern California and the Los Angeles County Department of Public Health, HIV and STD Program Office" ,  
    "2012 - 15", 
  "Data Analyst", 
    "Project Connect, Health Research Association, University of Southern California",  
    "2007 - 12",
) %>% 
  brief_entries(with  = company, what  = role, when  = dates)
```

\newpage

# Academic leadership
* **Data Science Program Coordinator** (2014-Present)
    - In collaboration with the Department of Computer Science, I developed the Undergraduate Certificate in Data Science at CSU, Chico. Program started Fall 2018
    - Currently working to expand into the Freshman/GE and Graduate space; Create a student internship program, and fee-based data-services practice. 
    - Website developer and maintainer for campus based website (https://www.csuchico.edu/datascience) and external blog based website (http://datascience.csuchico.edu)
* **DataFest Event Coordinator** (2018-Present)
  - Organize and host the annual DataFest at Chico State, a weekend long data hackathon where teams of undergraduate students tackle a suprise real world dataset and compete for fame and prizes. 
  - Website: https://chicodatafest.netlify.app/ 


# Teaching 

I regularly teach Applied and Theoretical Statistics courses, Data Science courses, and applied research/data science internships. The majority of my teaching materials are published through Github and available on my course website. 

$\vspace{1mm}$

* **General Education**
  - Statistics (Math 105) - General Education
* **Statistics**
  - Applied Statistics I (Math 315) - Non Majors, mostly Natural Sciences
  - Applied Statistics II (Math 456) - Majors, Minors, Data Science Certificate
  - Probability and Statistics I (Math 350) - Calculus & simulation based probability for all math & some engineering majors.
* **Data Science**: _All courses listed were developed and introduced by me as part of the Data Science Certificate._
  - Introduction to R (Math 130) - 5 week short course
  - Introduction to Data Science (Math 385)
  - Advanced Topics in Data Science (Math 485)
  - Data Science Project Capstone/Internship (Math 490)


* **Data Skills Workshops**
In addition to teaching traditional courses, I occasionally teach reproducible research and data analysis skills using R at workshops. I am a certified [Carpentry Instructor](https://carpentries.org/). 

```{r, eval=FALSE}
wk <- read.csv("workshops.csv", header=TRUE) %>% arrange(desc(when))
wk %>% 
          detailed_entries(when = when, 
                           what = title,
                           with = loc, 
                           where = org, 
                            why = details)
```


# Grants & Contracts

```{r}
gc <- read.csv("grants.csv", header=TRUE) %>% arrange(desc(dates)) %>%
       mutate(with = paste(type, amount))
gc %>% detailed_entries(when = dates, 
                        what = grant, 
                        where = title, 
                        with = with,
                        why  = details)
```

\newpage

# Consulting
I often consult with internal and external people and organizations to provide Statistical or Data Science assistance that do not directly result in a manuscript. 

```{r}
consulting <- read.csv("consulting.csv", header=TRUE) %>% arrange(desc(when))
consulting %>% detailed_entries(when = when, 
                                what = with, 
                                with = loc, 
                                why = details)
```


# Professional Society Memberships

```{r memberships}
tribble(
  ~ dates, ~ company, ~ role, 
  "2007 - Present", "American Statistical Association", 
    "Member: Sections on Statistics and Data Science Education, Statistical Programmers and Analysts, Teaching Statistics in Health Sciences",
  "2012 - 2013", "Western Users of SAS Software", 
    "Student Member",
  "2011 - 2013", "American Public Health Association", 
    "Member: Section on Public Health Statistics"
) %>% 
 brief_entries(what  = company, 
                   when  = dates,
                   with = role)
```

# Professional Service

```{r}
read.csv("prof-service.csv", header=TRUE) %>% 
  arrange(desc(dates)) %>% 
  brief_entries(when = dates, 
                what = bold, 
                with = right)
```

\newpage
# Publications

```{r bibfiles}
pubs <- bibliography_entries("pubs.bib")
```

## Books

```{r books}
pubs %>%
  filter(type == "book") 
```

## Manuscripts

```{r}
pubs %>%
  filter(type == "article-journal") %>%
  arrange(desc(issued))
```

## Presentations

```{r talks}
pubs %>%
  filter(type == "paper-conference") %>%
  arrange(desc(issued))
```
